Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2014-01-20 limits/ms.tex
Added shape plots.

% From aastex.cls
\newcommand\plotone[1]{%
 \centering
 \leavevmode
 \includegraphics[width={\columnwidth}]{#1}%
}%
\newcommand\plottwo[2]{{%
 \centering
 \leavevmode
 \columnwidth=.45\columnwidth
 \includegraphics[width={\columnwidth}]{#1}%
 \hfil
 \includegraphics[width={\columnwidth}]{#2}%
}}%
\newcommand\plotthree[3]{{%
 \centering
 \leavevmode
 \columnwidth=.30\columnwidth
 \includegraphics[width={\columnwidth}]{#1}%
 \hfil
 \includegraphics[width={\columnwidth}]{#2}%
 \hfil
 \includegraphics[width={\columnwidth}]{#3}%
}}%

@@

@@

\begin{figure}
\plotone{BCZContrastR1R3_TmS_shape.pdf}
\caption{}
\label{}
\end{figure}

>>>>

% From aastex.cls
\newcommand\plotone[1]{%
 \centering
 \leavevmode
 \includegraphics[width={\columnwidth}]{#1}%
}%
\newcommand\plottwo[2]{{%
 \centering
 \leavevmode
 \columnwidth=.45\columnwidth
 \includegraphics[width={\columnwidth}]{#1}%
 \hfil
 \includegraphics[width={\columnwidth}]{#2}%
}}%
\newcommand\plotthree[3]{{%
 \centering
 \leavevmode
 \columnwidth=.30\textwidth
 \includegraphics[width={\columnwidth}]{#1}%
 \hfil
 \includegraphics[width={\columnwidth}]{#2}%
 \hfil
 \includegraphics[width={\columnwidth}]{#3}%
}}%

@@

\begin{figure*}
\plotthree{AAExtendedDoubleR1_TmS-shape-hist-11.pdf} {AAferror_shape-1sig.pdf} {BBferror_shape-1sig.pdf}\\
\plotthree{BCZContrastR1R3_TmS-shape-hist-212.pdf} {ACferror_shape-1sig.pdf} {BCferror_shape-1sig.pdf}
\caption{ The two plots in the left most column show sample distributions of
  $s=\lambda_1/\lambda_2$, the ratio of the largest to smallest principal axes.
  The upper (poor) plot is from the DMdom/DMshallow galaxy, while the lower (good) plot is
  from the Sdom/DMcuspy galaxy. The black vertical lines mark the $1\sigma$
  region and the vertical blue line is the value of $s$ for the corresponding
  mock galaxy. The remain four plots are similar to those in \figref{main
  results pixel-wise} and show the fractional error of $s$ over all the models,
with respect to the mock galaxies.}

\label{main results pixel-wise}
\end{figure*}

@@
